Verified Time Balancing of Securit Protocols

### 2019-01-16 Src/talk.tex
Need to look at prf for Do, and how to manage arrays

\begin{frame}[fragile]
  \frametitle{The Problem}
  \begin{itemize}
    \item Can we formally prove that an implementation of
            a network security protocol is immune to 
                  timing side-channel attacks?
    \item In other words, can we show that a model of the protocol,
            along with its implementation is unable to leak
                  any timing information to an observer.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Rationale}
  \begin{itemize}
    \item Some departments in the ASD spend a large amount of time
            manually verifying cryptographic routines in vendor
            code.
    \item Requires large amounts of time and expertise, resulting
            in a slow verfication process.
    \item Formal methods may allow the 
            automation of these verification processes.
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{How do proof assistants work?}
    \begin{itemize}
      \item Rely on on a relationship between proofs in mathematics
              and computer programs known as the Curry-Howard 
                    correspondance.
      \item The proof system of intuitionistic 
              natural deduction can be directly interpreted 
                    as a model of computation known as 
                    lambda calculus.
    \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{A diagram of Prg.}
\end{frame}

>>>>

\begin{frame}[fragile]
  \frametitle{The Problem}
  \begin{itemize}
    \item Can we formally prove that an implementation of
            a network security protocol is immune to 
                  timing side-channel attacks?
    \item In other words, can we show that a model of the protocol,
            along with its implementation is unable to leak
                  any timing information to an observer.
    \item Some Example?
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Rationale}
  \begin{itemize}
    \item Some departments in the ASD spend a large amount of time
            manually verifying cryptographic routines in vendor
            code.
    \item Requires large amounts of time and expertise, resulting
            in a slow verfication process.
    \item Formal methods may allow progress towards the 
            automation of these verification processes.
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{How do proof assistants work?}
    \begin{itemize}
      \item Rely on on a relationship between proofs in mathematics
              and computer programs known as the Curry-Howard 
                    correspondance.
      \item The proof system of intuitionistic 
              natural deduction can be directly interpreted 
                    as a model of computation (lambda calculus).
    \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{A diagram of Prg syntax.}
   How should I represent this?
\end{frame}

\begin{frame}[fragile]
